---
title: "workflow"
format:
  html:
    toc: true
editor: visual
---

::: callout-note
## Alert

This is some information that you should pay attention to about the MLIT dataset analysis.
:::

The objective of this web page is twofold:

-   to clean and explore the MLIT which will be the main one for my master's thesis and

<!-- -->

-   to learn QGIS and generate risk maps and real estate price maps, and their correlation.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  results = 'hide',
  message = FALSE,
  warning = FALSE
)
```

### The MLIT Dataset

Data can be found on the MLIT Dataset : <https://www.reinfolib.mlit.go.jp/realEstatePrices/>. It contains all the real estates price transactions all over Japan since 2003.

### Packages

Below are the packages you need to install if you want the following code to work:

```{r}
library(tidyverse)
library(readr)
library(haven)
```

### Import

I use the data already cleaned by Ikefuji & al. for a first analysis. I then will clean it myself.

```{r}
library(readr)

#df_raw <- read_csv("/Users/anthony/Desktop/master_thesis/data/raw/mlit/28_Hyogo_Prefecture_20053_20252_en_fixed.csv")
#df <- df_raw
```

### Summary

First, Let's take a look at the MLIT dataset by printing the first 10 rows:

```{r}
#df |>
#  mutate(N = 10)
```
