---
title: "Workflow"
---

## Data wrangling

### The MLIT Dataset

The data used in this analysis comes from the [MLIT Dataset](https://www.reinfolib.mlit.go.jp/realEstatePrices/), which contains records of real estate price transactions across Japan since 2003.

You can select the prefectures you want to download. I chose to download all of them and ended up with 47 datasets, corresponding to the 47 prefectures of Japan.

### Loading the data

I use Stata to combine the 47 datasets and save the big one file as `data_mlit`, since Stata is more convenient for handling encoding issues.

```{stata}
#| eval: false
cd "/Users/anthony/Desktop/master_thesis/data/raw/mlit"

local prefectures : dir "." files "*.csv"
clear

foreach prefecture of local prefectures {
	preserve
	import delimited "`f'", clear
	tempfile temp
	save `temp'
	restore 
	append using `temp'
}

save data_mlit, replace
```

For the cleaning part, I go back using R. Let's clean this database!

## Data cleaning

More coding samples will be available soon.

```{r}
# Example plot
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Car Weight vs MPG")
```

## Analysis

```{r}
library(ggplot2)
```

Look forward for the results!

------------------------------------------------------------------------

[Back to Home](index.html)
